Java Based Memory Latency Simulator

### 2020-11-14 finalPaper/paper.tex
Added hyperef package

% 
% Sample latex source for a project report
%
% This is intended as an introduction to latex, but includes some
% advice about what you might want for the content of your paper
%
% Jim Teresco
% Williams College, Mount Holyoke College, Siena College, The College
% of Saint Rose
%
% Last modified: Mon Dec  4 19:03:24 EST 2017
%
%
% Modified by: Pat Baumgardner, Adam Dachenhausen, Shah Syed
%
%
% First, as you may have guessed, % is the way to define a latex 
% comment
%
% The first line tells latex you want for a default font size and that
% you want to create an ``article''
\documentclass[12pt]{article}
% extra packages to bring in
\usepackage{latexsym}
\usepackage{graphicx}      % extended graphics package
\usepackage{epsfig}        % wrapper for graphicx package
\usepackage{times}
\usepackage{url}
% set some margins, these can be defined as in, cm, pt
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}

@@

% Abstract!
\begin{abstract}
It's usually a good idea to include an abstract.  This should be a
brief summary of your paper.  Highlight your important results.  A
half a page is about right.  Maybe less.  It should be independent of
your subsequent introduction/overview section.
\end{abstract}

@@

Insert instructions on how to run and build here.

>>>>

% 
% Sample latex source for a project report
%
% This is intended as an introduction to latex, but includes some
% advice about what you might want for the content of your paper
%
% Jim Teresco
% Williams College, Mount Holyoke College, Siena College, The College
% of Saint Rose
%
% Last modified: Mon Dec  4 19:03:24 EST 2017
%
%
% Modified by: Pat Baumgardner, Adam Dachenhausen, Shah Syed
%
%
% First, as you may have guessed, % is the way to define a latex 
% comment
%
% The first line tells latex you want for a default font size and that
% you want to create an ``article''
\documentclass[12pt]{article}
% extra packages to bring in
\usepackage{latexsym}
\usepackage{graphicx}      % extended graphics package
\usepackage{epsfig}        % wrapper for graphicx package
\usepackage{times}
\usepackage{url}
\usepackage{hyperef}
% set some margins, these can be defined as in, cm, pt
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}

@@

% Abstract!
\begin{abstract}

Insert abstract here.

\end{abstract}

@@

The simulator is written in Java, and therefore, you will need to have
Java installed to run it. See \href{https://www.java.com/en/download/}
{Java Download} for more.
